---
title: "Connect R to a Database"
output: html_notebook
author: Nana Boateng
df_print: paged
Time: '`r Sys.time()`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

https://stackoverflow.com/questions/39401230/connect-r-to-a-sql-server-database-engine

```{r}
library("RODBC")
#library("XLConnect")

dbhandle <- odbcDriverConnect('driver={SQL Server};server=Name_Of_Server;database=Name_Of_DB;trusted_connection=true')
currTableSQL<-paste("SELECT * From Your_Table",sep="")
currTableDF<-sqlQuery(dbhandle,currTableSQL)

```



```{r}
library(RODBC)
dbconnection <- odbcDriverConnect("Driver=ODBC Driver 11 for SQL Server;Server=YourDBName\\SQLEXPRESS; Database=TestDB;Uid=; Pwd=; trusted_connection=yes")
initdata <- sqlQuery(dbconnection,paste("select * from MyTable;"))
odbcClose(channel)
```


2.1 Making a connection
ODBC works by setting up a connection or channel from the client (here RODBC) to the DBMSs as specified in the DSN. Such connections are normally used throughout a session, but should be closed explicitly at the end of the session—however RODBC will clear up after you if you forget (with a warning that might not be seen in a GUI environment). There can be many simultaneous connections.
The simplest way to make a connection is
```{r}

library(RODBC)
ch <- odbcConnect("some dsn")
#and when you are done with it,
close(ch)
# or if you prefer
odbcClose(ch)
```
If the DBMS user and password are needed and not stored in the DSN, they can be supplied by e.g.
```{r}

ch <- odbcConnect("some dsn", uid = "user", pwd = "****")
```

Some drivers will return all visible table-like objects, not just those owned by you. In that case you may want to restrict the scope by e.g.
```{r}
sqlTables(ch, tableType = "TABLE") 
sqlTables(ch, schema = "some pattern") 
sqlTables(ch, tableName = "some pattern")
```



```{r}
library(RSQLServer)
SQLServer()
    ## S4 method for signature 'SQLServerDriver'
dbConnect(drv, server, file = NULL,
      database = NULL, type = NULL, port = NULL, properties = NULL)



## Not run:
    SQLServer()
    ## End(Not run)
    # View sql.yaml file bundled in package
    file <- system.file("extdata", "sql.yaml", package = "RSQLServer")
    readLines(file)
    # Connect using ~/sql.yaml file
    ## Not run:
    if (have_test_server()) {
     dbConnect(RSQLServer::SQLServer(), "TEST")
    }
    # Example where ~/sql.yaml does not exist or where the server
    # is not in the YAML file.
    dbConnect(RSQLServer::SQLServer(), server="11.1.111.11", port=1434,
       properties=list(useNTLMv2="true", domain="myco", user="me",
         password="asecret"))


```


```{r}
library(RJDBC)

 ## Not run:
    drv <- JDBC("com.mysql.jdbc.Driver",
      "/etc/jdbc/mysql-connector-java-3.1.14-bin.jar", " ")
    conn <- dbConnect(drv, "jdbc:mysql://localhost/test")
    dbListTables(conn)
    data(iris)
    dbWriteTable(conn, "iris", iris)
    dbGetQuery(conn, "select count(*) from iris")
    d <- dbReadTable(conn, "iris")
    ## End(Not run)

```

