---
title: "Purrr and furrr Tutorial"
output: html_notebook
author: Nana Boateng
df_print: paged
Time: '`r Sys.time()`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup,include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      out.width ="100%",
                      message = FALSE)

```



```{r}
#install.packages(c('officer',"rvg"))


#install.packages(c("ggridges"))
```




```{r}
library(rvg)
library(ggplot2)
library(officer)
library(data.table)
library(ggridges)
library(tidyverse)
library(tidyquant)
library(officer)
library(rvg)
library(viridis)
library(purrr)
library(furrr)
library(scales)
# NOT RUN {
# Convert factors to characters
iris %>%
  map_if(is.factor, as.character) %>%
  str()

```


```{r}
# Specify which columns to map with a numeric vector of positions:
mtcars %>% map_at(c(1, 4, 5), as.character) %>% str()

# Or with a vector of names:
mtcars %>% map_at(c("cyl", "am"), as.character) %>% str()


```


```{r}
# Specify which columns to map with a numeric vector of positions:
mtcars %>% furrr::future_map_at(c(1, 4, 5), as.character) %>% str()

# Or with a vector of names:
mtcars %>% furrr::future_map_at(c("cyl", "am"), as.character) %>% str()

```




list_modify(.x, ...)/update_list(x, z1 = ~z[[1]])  modify a list like add new members.
```{r}
list(x = rbernoulli(100), y = 1:100) %>%
  transpose() %>%
  map_if("x", ~ update_list(., y = ~ y * 100)) %>%
  transpose() %>%
  simplify_all()
```


```{r}
list(x = rbernoulli(100), y = 1:100) %>%
  transpose() %>%
  furrr::future_map_if("x", ~ update_list(., y = ~ y * 100)) %>%
  transpose() %>%
  simplify_all()

```



```{r}
library(purrr)
# A more realistic example: split a data frame into pieces, fit a
# model to each piece, summarise and extract R^2
mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt,.)) 

```


```{r}
# A more realistic example: split a data frame into pieces, fit a
# model to each piece, summarise and extract R^2
mtcars %>%
  split(.$cyl) %>%
  furrr::future_map(~ lm(mpg ~ wt,.))
```




```{r}
models <- mtcars %>%
split(.$cyl) %>%
map(function(df) lm(mpg ~ wt, data = df))
models
```

```{r}
models <- mtcars %>%
split(.$cyl)

models %>%
map(~lm(mpg ~ wt, data = .))

```


```{r}
x=list(a=c(2,4,5),b=c(5,6,8,9))

sapply(x,mean)


x%>%
map_df(.,mean)%>%
  simplify_all()

```

```{r}
library(purrr)

mtcars %>%
  split(.$cyl) %>% # from base R
  map(~ lm(mpg ~ wt, data = .)) %>%
  map(summary) %>%
  map_dbl("r.squared")
```

```{r}
mtcars %>%
  split(.$cyl) %>% # from base R
  furrr::future_map(~ lm(mpg ~ wt, data = .)) %>%
 furrr::future_map(summary) %>%
  furrr::future_map_dbl("r.squared")
```




```{r}
# Split into pieces, fit model to each piece, then predict
by_cyl <- mtcars %>% split(.$cyl)
mods <- by_cyl %>% map(~ lm(mpg ~ wt, data = .))
map2(mods, by_cyl, predict)

```




create 10 list of size 10 each and find the mean of each
```{r}
set.seed(1)
# NOT RUN {
1:10 %>%
  map(rnorm, n = 10)%>%
  map_dbl(mean) 

# Or use an anonymous function
1:10 %>%
  map(function(x) rnorm(10, x))%>%
  map_dbl(mean) 


# Or a formula
1:10 %>%
  map(~ rnorm(10, .x))%>%
  map_dbl(mean) 

 
# Or a formula
1:10 %>%
  map(~ rnorm(10, .x))%>%
future_imap_dbl(mean) 

```


```{r}
# Vectorizing a function over multiple arguments
df <- data.frame(
  x = c("apple", "banana", "cherry"),
  pattern = c("p", "n", "h"),
  replacement = c("x", "f", "q"),
  stringsAsFactors = FALSE
  )
pmap(df, gsub)
pmap_chr(df, gsub)

furrr::future_imap_chr(df, gsub)

furrr::future_imap(df, gsub)

```




```{r}
m=matrix(0,10,10)
for (i in 1:10){
  
m[i,]=rnorm(10)  
}
m

m=list()
for (i in 1:10){
  
m[[i]]=rnorm(10)   
}
m

```




```{r}
# Extract by name or position
# .default specifies value for elements that are missing or NULL
l1 <- list(list(a = 1L), list(a = NULL, b = 2L), list(b = 3L))
l1 %>% map("a", .default = "???")
l1 %>% map_int("b", .default = NA)
l1 %>% map_int(2, .default = NA)
l1
```

keep elements in second position in each list.
```{r}
#
# Supply multiple values to index deeply into a list
l2 <- list(
  list(num = 1:3,     letters[1:3]),
  list(num = 101:103, letters[4:6]),
  list()
)
l2%>% map(c(2, 2)) 

```

select the third element in each num list
```{r}
# Use a list to build an extractor that mixes numeric indices and names,
# and .default to provide a default value if the element does not exist
l2
l2 %>% map(list("num", 3))

```


```{r}
# A more realistic example: split a data frame into pieces, fit a
# model to each piece, summarise and extract R^2
mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x)) %>%
  map(summary) %>%
  map_dbl("r.squared")
```



```{r}
# Use map_lgl(), map_dbl(), etc to reduce to a vector.
# * list
# Use map_lgl(), map_dbl(), etc to reduce to a vector.
# * list
mtcars %>% map(sum)
# * vector
mtcars %>% map_dbl(sum)

apply(mtcars,2,sum)

```


```{r}
# If each element of the output is a data frame, use
# map_dfr to row-bind them together:
mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x)) %>%
  map_dfr(~ as.data.frame(t(as.matrix(coef(.)))))
# (if you also want to preserve the variable names see
# the broom package)
# }
```

```{r}
# A more realistic example: split a data frame into pieces, fit a
# model to each piece, summarise and extract R^2
m=mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x))%>%map("coefficients")%>%as.data.frame()%>%t()

rownames(m)<-c()
m%>%data.frame()
#m[[1]]$coef
#library(tibble)
#remove_rownames(m)

```

keep() and discard() allow you to filter a vector based on a predicate function. compact() is a helpful wrapper that throws away empty elements of a list.
```{r}
1:10 %>% keep(~. %% 2 == 0)

1:10 %>% discard(~. %% 3 == 0)


list(list(x = TRUE, y = 10), list(x = FALSE, y = 20)) %>%
  keep("x") %>%
  str()

rep(10, 10) %>%
  map(sample, 5) %>%
  keep(function(x) mean(x) > 6)

```



```{r}
list(NULL, 1:3, NULL, 7) %>%
  compact() %>%
  str()
```



#### sweep
```{r}
require(stats) # for median
attitude%>%head()
med.att <- apply(attitude, 2, median)
med.att 
sweep(data.matrix(attitude), 2, med.att)  # subtract the column medians

```


```{r}
## More sweeping:
A <- array(1:24, dim = 4:2)

## no warnings in normal use

# subtract 5 from every element
sweep(A, 1, 5)

A


A.min<-apply(A,1,min)
A.min
sweep(A,1,1:3)
#subtract colmeans from each column of array
# first element of column subracts all first columns of array
#second element of column means subtract from second columns of array
B=matrix(1:12,nrow = 4)
M=colMeans(B)
M

A
sweep(A,2,M,FUN="-")

A-M
```



#### combine
Take a sequence of vector, matrix or data frames and combine into rows of a common data frame with an additional column source indicating the source object
```{r}
a  <-  matrix(rnorm(12),ncol=4,nrow=3)
b  <-  1:4
combine(a,b)


combine(x=a,b)
combine(x=a,y=b)
#combine(a,b,names=c("one","two")
c <- 1:6
combine(b,c)


rbind(a,b)


rbind.data.frame(a,b)


```

```{r}
#data.table::rbindlist(a,b,use.names=FALSE,fill=T)

## ---------------------------------------------------------------------
## COMBINING TWO MATRICES
## ---------------------------------------------------------------------
m <- matrix(1:20, nrow=5, dimnames=list(LETTERS[1:5], letters[1:4]))
combine(m[1:3,], m[4:5,])
combine(m[1:3, 1:3], m[3:5, 3:4]) # overlap

m
as.vector(m)
```

setNames

```{r}
## ---------------------------------------------------------------------
## setNames
## ---------------------------------------------------------------------
setNames( 1:3, c("foo", "bar", "baz") )

# this is just a short form of
tmp <- 1:3
names(tmp) <-  c("foo", "bar", "baz")
tmp
```

#### Plotting a list of ggplots and saving them all at the same time.


```{r}
library(ggplot2)
p<-mtcars%>%
  split(.$cyl)%>%
  map(~ggplot(.,aes(mpg,wt))+geom_point())

paths<-stringr::str_c(names(p),".pdf")

#paste(names(p),".pdf")

#pwalk(list(paths,p),ggsave,path="/Users/nanaakwasiabayieboateng/Documents/memphisclassesbooks/ggplot2")

pmap(list(paths,p),ggsave,path="/Users/nanaakwasiabayieboateng/Documents/memphisclassesbooks/ggplot2")

```



```{r}
# find the first element where predicate is true
ind=round(rnorm(20))
diff(ind)%>%detect(~.==1)


diff(ind)%>%detect_index(~.==1)
```


#### Aggregate


## S3 method for class 'formula'
aggregate(formula, data, FUN, ...,
          subset, na.action = na.omit)

## S3 method for class 'ts'
aggregate(x, nfrequency = 1, FUN = sum, ndeltat = 1,
          ts.eps = getOption("ts.eps"), ...)

```{r}
## Dot notation:

iris%>%head()
aggregate(. ~ Species, data = iris, mean)


## Formulas, one ~ one, one ~ many, many ~ one, and many ~ many:

chickwts%>%head
aggregate(weight ~ feed, data = chickwts, mean)
#alternatively
aggregate(. ~ feed, data = chickwts, mean)

```

#### Imputing missing values in parallel using {furrr}

```{r}
library(mice)

data(boys)

brotools::describe(boys) %>%
  select(variable, type, n_missing, everything())
```

```{r}
start <- Sys.time()
imp_boys <- mice(boys, m = 10, maxit = 100, printFlag = FALSE)
end <- Sys.time() - start


imp_boys <- mice::complete(imp_boys, "long")

print(end)



```




```{r}
library(mice)
start <- Sys.time()
imp_boys_purrr <- map(rep(1, 10), ~mice(data = boys, m = ., maxit = 100, printFlag = FALSE))
end <- Sys.time() - start

print(end)

imp_boys_purrr_complete <- map(imp_boys_purrr, mice::complete)

```




```{r}
imp_boys_purrr <- map2(.x = seq(1,10), .y = imp_boys_purrr_complete, ~mutate(.y, imp_id = as.character(.x)))
```




```{r}
imp_boys_purrr <- bind_rows(imp_boys_purrr)

rbindlist(imp_boys_purrr)
```



```{r}
#devtools::install_github("DavisVaughan/furrr")
library(furrr)
plan(multiprocess)

start <- Sys.time()
imp_boys_future <-future_map(rep(1, 10), ~mice(data = boys, m = ., maxit = 100, printFlag = FALSE))
end <- Sys.time() - start

print(end)
```



```{r}
imp_boys_future_complete <- map(imp_boys_future, mice::complete)

imp_boys_future <- map2(.x = seq(1,10), .y = imp_boys_future_complete, ~mutate(.y, imp_id = as.character(.x)))

imp_boys_future <- bind_rows(imp_boys_future)

imp_boys_future %>%
  brotools::describe() %>%
  select(variable, type, n_missing, everything())
```


```{r}

start <- Sys.time()
library(parallelMap)
parallelStartSocket(2) 
parallelStartMulticore(cpus=6)# start in socket mode and create 2 processes on localhost
f = function(i){
  #map(i, mice(data = boys, m = ., maxit = 100, printFlag = FALSE))
  mice(boys, m = i, maxit = 100, printFlag = FALSE)
} 

# define our job
y = parallelMap(f, rep(1,10)) # like R's Map but in parallel

parallelStop()
end <- Sys.time() - start

print(end)

```





```{r}
#devtools::install_github("b-rodrigues/parlMICE")
```

