---
title: "randomForest  Explainer
"
output: html_notebook
author: Nana Boateng
df_print: paged
Time: '`r Sys.time()`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

 
```{r,message=FALSE,warning=FALSE}
library(randomForestExplainer)
library(randomForest)
library(tidyverse)
```
 
 
####  explain_forest Explain a random forest

Explains a random forest in a html document using plots created by randomForestExplainer

```{r,message=FALSE,warning=FALSE}
#install.packages("randomForestExplainer")



forest <- randomForest::randomForest(Species ~ ., data = iris, localImp = TRUE)



#explain


suppressPackageStartupMessages(suppressMessages(suppressWarnings(explain_forest(forest, interactions = TRUE))))

#suppressWarnings()

```



#### important_variables Extract k most important variables in a random forest

Get the names of k variables with highest sum of rankings based on the specified importance mea- sures


```{r}
important_variables(measure_importance(forest), k = 3)
```


#### measure_importance 

Importance of variables in a random forest


      measure_importance(forest, mean_sample = "top_trees", measures = NULL)

mean_sample has value "all_trees", "top_trees", "relevant_trees"

```{r}
measure_importance(forest)
```



#### min_depth_distribution

Calculate minimal depth distribution of a random forest

```{r}
min_depth_distribution(forest)%>%head()
```



#### min_depth_interactions

Calculate mean conditional minimal depth with respect to a vector of variables


      min_depth_interactions(forest,
      vars = important_variables(measure_importance(forest)),
      mean_sample = "top_trees", uncond_mean_sample = mean_sample)


```{r}


forest <- randomForest::randomForest(Species ~ ., data = iris, ntree = 100)
min_depth_interactions(forest, c("Petal.Width", "Petal.Length"))%>%head()

```



#### plot_importance_ggpairs

Plot importance measures with ggpairs
Plot selected measures of importance of variables in a forest using ggpairs

      plot_importance_ggpairs(importance_frame,
      measures = names(importance_frame)[c(2, 4, 5, 3, 7)],
      main = "Relations between measures of importance")

```{r}
forest <- randomForest::randomForest(Species ~ ., data = iris, localImp = TRUE, ntree = 200) 

frame <- measure_importance(forest, measures = c("mean_min_depth", "times_a_root"))

plot_importance_ggpairs(frame, measures = c("mean_min_depth", "times_a_root"))

```




#### plot_importance_rankings

Plot importance measures rankings with ggpairs
Description
Plot against each other rankings of variables according to various measures of importance

    plot_importance_rankings(importance_frame,
      measures = names(importance_frame)[c(2, 4, 5, 3, 7)],
      main = "Relations between rankings according to different measures")
      
      
```{r}

forest <- randomForest::randomForest(Species ~ ., data = iris, localImp = TRUE, ntree = 300) 

frame <- measure_importance(forest, measures = c("mean_min_depth", "times_a_root"))

plot_importance_ggpairs(frame, measures = c("mean_min_depth", "times_a_root"))

```
      
      
      
      
#### plot_min_depth_distribution
Plot the distribution of minimal depth in a random forest
Description
Plot the distribution of minimal depth in a random forest

        plot_min_depth_distribution(min_depth_frame, k = 10, min_no_of_trees = 0,
         mean_sample = "top_trees", mean_scale = FALSE, mean_round = 2,
        main = "Distribution of minimal depth and its mean") 
        
        
```{r}
 forest <- randomForest::randomForest(Species ~ ., data = iris, ntree = 300)
    plot_min_depth_distribution(min_depth_distribution(forest))

```
        


####  plot_min_depth_interactions
Plot the top mean conditional minimal depth


    plot_min_depth_interactions(interactions_frame, k = 30,
      main = paste0("Mean minimal depth for ", paste0(k,
      " most frequent interactions"))) 
      
      
```{r}

forest <- randomForest::randomForest(Species ~ ., data = iris, ntree = 100)

plot_min_depth_interactions(min_depth_interactions(forest, c("Petal.Width", "Petal.Length")))

```
      


#### plot_multi_way_importance

Multi-way importance plot

Plot two or three measures of importance of variables in a random fores. Choose importance mea- sures from the colnames(importance_frame). 

```{r}
forest <- randomForest::randomForest(Species ~ ., data = iris, localImp = TRUE)
plot_multi_way_importance(measure_importance(forest))
```





#### plot_predict_interaction

Plot the prediction of the forest for a grid of values of two numerical variables

 Plot the prediction of the forest for a grid of values of two numerical variables

```{r}

    forest <- randomForest::randomForest(Species ~., data = iris)
    plot_predict_interaction(forest, iris, "Petal.Width", "Sepal.Width")
    
```

