---
title: "Scales"
output: html_notebook
---


```{r}
library(scales)
library(Hmisc)
```




```{r}
one = c(1:5)

paste0(one,"")

paste(one,"")


paste0(one,sep= ",")


paste0(one,collapse = "")

cat(paste(shQuote(one, type="cmd"), collapse=", "))



```


```{r}
paste0(one,sep= "")
```


```{r}
cat(paste0(shQuote(one, type="cmd"), collapse=", "))

```

```{r}
paste0(sprintf("'%d'", 1:4), collapse = ", ")
```



```{r}
dput(as.character(one))
paste(shQuote(one), collapse=", ")

write.table(matrix(as.character(one),nrow=1), sep=",",
              row.names=FALSE, col.names=FALSE)

write.csv(matrix(as.character(one),nrow=1),row.names=FALSE)


```




```{r}
paste("'",as.character(one),"'",collapse=", ",sep="")

rs <- paste("\"",as.character(one),"\"",collapse=", ",sep="")
cat(rs)
```


```{r}
one = c(1:5)



Hmisc::Cs(a,b,c,d)


predictor=Hmisc::Cs( Age, Employment.Primarily.retired..or, Employment.Unable.to.work., race_white.Yes, Employment.Self.employed.)

predictor

```



```{r}
comma_format()(c(1, 1e3, 2000, 1e6))
comma_format(digits = 9)(c(1, 1e3, 2000, 1e6))
comma(c(1, 1e3, 2000, 1e6))


```


```{r}
# If you're European you can switch . and , with the more general
# format_format
point <- format_format(big.mark = ".", decimal.mark = ",", scientific = FALSE)
point(c(1, 1e3, 2000, 1e6))
point(c(1, 1.021, 1000.01))
```




```{r}
pretty_breaks()(1:10)
pretty_breaks()(1:100)

```

```{r}
pretty_breaks()(as.Date(c("2008-01-01", "2009-01-01")))
pretty_breaks()(as.Date(c("2008-01-01", "2090-01-01")))
```



```{r}
library(ggplot2)
library(scales)       
ggplot(diamonds) + geom_point(aes(x = carat, y =  price)) + scale_y_continuous(labels = dollar_format(suffix = "€", prefix = ""))
```

```{r}
library(ggplot2)
library(scales)       
ggplot(diamonds) + geom_point(aes(x = carat, y =  price)) + scale_y_continuous(labels = dollar_format(suffix = "", prefix = "$"))
```



```{r}
library(ggplot2)
library(scales)       
ggplot(diamonds) + geom_point(aes(x = carat, y =  price)) + scale_y_continuous(labels = percent_format())
```




Modify colour transparency. Vectorised in both colour and alpha

```{r}
alpha("red", 0.1)
alpha(colours(), 0.5)
#alpha("red", seq(0, 1, length.out = 10))
```


Point area palette (continuous).

```{r}
area_pal(range = c(1, 6))
```


```{r}
show_col(brewer_pal()(10))
    show_col(brewer_pal("div")(6))
    

```


```{r}
show_col(brewer_pal(palette = "Greens")(5))
    # Can use with gradient_n to create a continous gradient
    cols <- brewer_pal("div")(5)
    show_col(gradient_n_pal(cols)(seq(0, 1, length.out = 30)))
```


Compute breaks for continuous scale.

cbreaks(range, breaks = extended_breaks(), labels = scientific_format())

```{r}
 cbreaks(c(0, 100))
    cbreaks(c(0, 100), pretty_breaks(3))
    cbreaks(c(0, 100), pretty_breaks(10))
    cbreaks(c(1, 100), log_breaks())
    cbreaks(c(1, 1e4), log_breaks())
    cbreaks(c(0, 100), labels = math_format())
    cbreaks(c(0, 1), labels = percent_format())
    cbreaks(c(0, 1e6), labels = comma_format())
    cbreaks(c(0, 1e6), labels = dollar_format())
    cbreaks(c(0, 30), labels = dollar_format())
    # You can also specify them manually:
    cbreaks(c(0, 100), breaks = c(15, 20, 80))
    cbreaks(c(0, 100), breaks = c(15, 20, 80), labels = c(1.5, 2.0, 8.0))
    cbreaks(c(0, 100), breaks = c(15, 20, 80),
labels = expression(alpha, beta, gamma))
```



Censor any values outside of range.
censor(x, range = c(0, 1), only.finite = TRUE)

```{r}
censor(c(-1, 0.5, 1, 2, NA))
```


```{r}
censor(c(-3, 4.5, 1, 2, NA),range=c(-2,2))
```


Modify standard R colour in hcl colour space.
col2hcl(colour, h, c, l, alpha = 1)
```{r}

col2hcl(colors())
```



Fast color interpolation
colour_ramp(colors, na.color = NA, alpha = FALSE)

```{r}
#colour_ramp(colors(), na.color = NA, alpha = FALSE)
```


Color mapping

col_numeric(palette, domain, na.color = "#808080")
    col_bin(palette, domain, bins = 7, pretty = TRUE, na.color = "#808080")
    col_quantile(palette, domain, n = 4, probs = seq(0, 1, length.out = n + 1),
      na.color = "#808080")
    col_factor(palette, domain, levels = NULL, ordered = FALSE,
      na.color = "#808080")
      
      
```{r}
pal <- col_bin("Greens", domain = 0:100)
    show_col(pal(sort(runif(10, 60, 100))))
    # Exponential distribution, mapped continuously
    show_col(col_numeric("Blues", domain = NULL)(sort(rexp(16))))
    # Exponential distribution, mapped by interval
    show_col(col_bin("Blues", domain = NULL, bins = 4)(sort(rexp(16))))
    # Exponential distribution, mapped by quantile
    show_col(col_quantile("Blues", domain = NULL)(sort(rexp(16))))
    # Categorical data; by default, the values being colored span the gamut...
    #show_col(col_factor("RdYlBu")(LETTERS[1:5]))
    # ...unless the data is a factor, without droplevels...
    #show_col(col_factor("RdYlBu", domain = NULL)(factor(LETTERS[1:5], levels=LETTERS)))
    # ...or the domain is stated explicitly.
    #show_col(col_factor("RdYlBu", levels = LETTERS)(LETTERS[1:5]))
```



Continuous scale.
cscale(x, palette, na.value = NA_real_, trans = identity_trans())

```{r}
with(mtcars, plot(disp, mpg, cex = cscale(hp, rescale_pal())))
    with(mtcars, plot(disp, mpg, cex = cscale(hp, rescale_pal(),
      trans = sqrt_trans())))
    with(mtcars, plot(disp, mpg, cex = cscale(hp, area_pal())))
    with(mtcars, plot(disp, mpg, pch = 20, cex = 5,
      col = cscale(hp, seq_gradient_pal("grey80", "black"))))
```



Regularly spaced dates.date_breaks(width = "1 month")

Formatted dates.date_format .date_format(format = "%Y-%m-%d", tz = "UTC")
```{r}
## by month
seq(as.Date("2000/1/1"), by = "month", length.out = 12)

date_breaks(width = "1 month")
```



```{r}
years <- seq(as.Date("1910/1/1"), as.Date("1999/1/1"), "years")

seq.Date(as.Date("1910/1/1"), as.Date("1999/1/1"),"month")
## first days of years
seq(as.Date("1910/1/1"), as.Date("1999/1/1"), "years")
## by month
seq(as.Date("2000/1/1"), by = "month", length.out = 12)
## quarters
seq(as.Date("2000/1/1"), as.Date("2003/1/1"), by = "quarter")


```




```{r}
years <- seq(as.Date("1910/1/1"), as.Date("1999/1/1"), "years")
    t <- date_trans()
    t$transform(years)
    t$inverse(t$transform(years))
    t$format(t$breaks(range(years)))
```

Dichromat (colour-blind) palette (discrete).
dichromat_pal(name)
```{r}
show_col(dichromat_pal("BluetoOrange.10")(10))
    show_col(dichromat_pal("BluetoOrange.10")(5))
    # Can use with gradient_n to create a continous gradient
    cols <- dichromat_pal("DarkRedtoBlue.12")(12)
    show_col(gradient_n_pal(cols)(seq(0, 1, length.out = 30)))
```



Discard any values outside of range.

 discard(x, range = c(0, 1))
 
 
 
```{r}
#discard(c(-1, 0.5, 1, 2, NA))
```



Diverging colour gradient (continous).

Description
Diverging colour gradient (continous).
Usage
    div_gradient_pal(low = mnsl("10B 4/6"), mid = mnsl("N 8/0"),
      high = mnsl("10R 4/6"), space = "Lab")
Arguments
low colour for low end of gradient.
mid colour for mid point
high colour for high end of gradient.
space colour space in which to calculate gradient. Must be "Lab" - other values are deprecated.

```{r}
x <- seq(-1, 1, length.out = 100)
    r <- sqrt(outer(x^2, x^2, "+"))
    image(r, col = div_gradient_pal()(seq(0, 1, length.out = 12)))
    image(r, col = div_gradient_pal()(seq(0, 1, length.out = 30)))
    image(r, col = div_gradient_pal()(seq(0, 1, length.out = 100)))
    library(munsell)
    image(r, col = div_gradient_pal(low =
       mnsl(complement("10R 4/6", fix = TRUE)))(seq(0, 1, length = 100)))

```


dollar_format Currency formatter: round to nearest cent and display dollar sign. Description
The returned function will format a vector of values as currency. Values are rounded to the nearest cent, and cents are displayed if any of the values has a non-zero cents and the largest value is less than largest_with_cents which by default is 100000.


Usage
    dollar_format(prefix = "$", suffix = "", largest_with_cents = 1e+05, ...,
      big.mark = ",", negative_parens = FALSE)
dollar(x)

```{r}
dollar_format()(c(-100, 0.23, 1.456565, 2e3))
    dollar_format()(c(1:10 * 10))
    dollar(c(100, 0.23, 1.456565, 2e3))
    dollar(c(1:10 * 10))
    dollar(10^(1:8))
    usd <- dollar_format(prefix = "USD ")
    usd(c(100, -100))
    euro <- dollar_format(prefix = "", suffix = "\u20ac")
    euro(100)
```


```{r}

finance <- dollar_format(negative_parens = TRUE)
    
finance(c(-100, 100))

euro <- dollar_format(prefix = "", suffix = "€")
euro(1:10)
```




dscale Discrete scale. Description
Discrete scale.
Usage
    dscale(x, palette, na.value = NA)
  Arguments
    x
    palette
    na.value
vector of discrete values to scale aesthetic palette to use
aesthetic to use for missing values


```{r}
with(mtcars, plot(disp, mpg, pch = 20, cex = 3,
      col = dscale(factor(cyl), brewer_pal())))
```


expand_range Expand a range with a multiplicative or additive constant.
Description
Expand a range with a multiplicative or additive constant.
Usage
    expand_range(range, mul = 0, add = 0, zero_width = 1)
  Arguments
    range
    mul
    add
    zero_width
exp_trans
Description
range of data, numeric vector of length 2 multiplicative constract
additive constant
distance to use if range has zero width

```{r}

expand_range(range=c(1,5), mul = 0.0, add = 1, zero_width = 1)
expand_range(range=c(1,5), mul = 0.0, add = 2, zero_width = 1)
expand_range(range=c(1,5), mul = 1, add = 1, zero_width = 1)

```


exp_trans
Description
range of data, numeric vector of length 2 multiplicative constract
additive constant
distance to use if range has zero width
Exponential transformation (inverse of log transformation).
  Exponential transformation (inverse of log transformation).
Usage
    exp_trans(base = exp(1))
    
    
    
    ```{r}
exp_trans(base = exp(1))
    
exp_trans(base = exp(100))  

exp(1)
```


extended_breaks Extended breaks. Uses Wilkinson’s extended breaks algorithm as im- plemented in the labeling package.
Description
Extended breaks. Uses Wilkinson’s extended breaks algorithm as implemented in the labeling
package.
Usage
    extended_breaks(n = 5, ...)
Arguments
n desired number of breaks
... other arguments passed on to extended

```{r}
extended_breaks(n=20)(1:10)

```

```{r}
extended_breaks(n=200)(1:100)%>%head(10)
```

format_format Format with using any arguments to format.
Description
If the breaks have names, they will be used in preference to formatting the breaks.
Usage
    format_format(...)
    
    
```{r}
format.Date("2017-07-28 ")
```



gradient_n_pal Arbitrary colour gradient palette (continous).
Description
Arbitrary colour gradient palette (continous).
Usage
    gradient_n_pal(colours, values = NULL, space = "Lab")
  Arguments
    colours
    values
space
grey_pal
Description
vector of colours
if colours should not be evenly positioned along the gradient this vector gives the position (between 0 and 1) for each colour in the colours vector. See rescale for a convience function to map an arbitrary range to between 0 and 1.
colour space in which to calculate gradient. Must be "Lab" - other values are deprecated.

```{r}

    #gradient_n_pal(colours(), values = NULL, space = "Lab")
```

grey_pal
Grey scale palette (discrete).
Description
  Grey scale palette (discrete).
Usage
    grey_pal(start = 0.2, end = 0.8)
Arguments
start gray value at low end of palette end gray value at high end of palette

```{r}
grey_pal(start = 0.2, end = 0.8)
    show_col(grey_pal()(25))
    show_col(grey_pal(0, 1)(25))
```

hms_trans Transformation for times (class hms).
Description
Transformation for times (class hms).
Usage
hms_trans()

```{r,warning=FALSE,message=FALSE}
#Examples
    if (require("hms")) {
    hms <- round(runif(10) * 86400)
    t <- hms_trans()
    t$transform(hms)
    t$inverse(t$transform(hms))
    t$breaks(hms)
    }
```

```{r}
 hms <- round(runif(10) * 86400)
    t <- hms_trans()
   
    hms
```

```{r}
 t$transform(hms)
   
```

```{r}
 t$inverse(t$transform(hms))
     
```

```{r}
t$breaks(hms)
```

hue_pal
Description
Hue palette (discrete).
Usage
Hue palette (discrete).
     hue_pal(h = c(0, 360) + 15, c = 100, l = 65, h.start = 0,
      direction = 1)
      
      
      
      
```{r}

    show_col(hue_pal()(4))
    show_col(hue_pal()(9))
    show_col(hue_pal(l = 90)(9))
    show_col(hue_pal(l = 30)(9))
    show_col(hue_pal()(9))
    show_col(hue_pal(direction = -1)(9))
    show_col(hue_pal()(9))
    show_col(hue_pal(h = c(0, 90))(9))
    show_col(hue_pal(h = c(90, 180))(9))
    show_col(hue_pal(h = c(180, 270))(9))
    show_col(hue_pal(h = c(270, 360))(9))
```



```{r}
  show_col(hue_pal()(100)[4])
```


identity_pal Identity palette. Description
Leaves values unchanged - useful when the data is already scaled.
Usage
identity_pal()
identity_trans Identity transformation (do nothing).
Description
Identity transformation (do nothing).
Usage
identity_trans()

```{r}
#identity_trans()
```


linetype_pal Line type palette (discrete).
Description
Based on a set supplied by Richard Pearson, University of Manchester
Usage
    linetype_pal()
    
    
    
    ```{r}
#linetype_pal()
    
```

log1p_trans Log plus one transformation.
Description
Log plus one transformation.
Usage
    log1p_trans()

```{r}

    trans_range(log_trans(), 1:10)
    trans_range(log1p_trans(), 0:9)
```

log_breaks Log breaks (integer breaks on log-transformed scales).
Description
Log breaks (integer breaks on log-transformed scales).
Usage
    log_breaks(n = 5, base = 10)
Arguments
n desired number of breaks base base of logarithm to use

```{r}
log_breaks()(c(1, 1e6))
log_breaks()(c(1, 1e5))
```



log_trans Log transformation.
Description
Log transformation.
Usage
    log_trans(base = exp(1))
Arguments
base base of logarithm

```{r}

    log_trans(base = exp(1))
```

manual_pal
Description
Manual palette (manual).
Usage
    manual_pal(values)
Arguments
Manual palette (manual).
 values vector of values to be used as a palette.
 
 
 
```{r}
#show_col(manual_pal())
```
math_format Add arbitrary expression to a label. The symbol that will be replace by the label value is .x.
Description
Add arbitrary expression to a label. The symbol that will be replace by the label value is .x.
Usage
    math_format(expr = 10^.x, format = force)
    
    
    
    
    ```{r}
math_format()(1:10)
    
```
```{r}
math_format(alpha + frac(1, .x))(1:10)
    
```
```{r}
math_format()(runif(10))
    
```
```{r}
math_format(format = percent)(runif(10))
```

muted Mute standard colour.
Description
Mute standard colour.
Usage
    muted(colour, l = 30, c = 70)
Arguments
colour character vector of colours to modify l new luminance
c new chroma

```{r}

    muted("red")
    muted("blue")
    show_col(c("red", "blue", muted("red"), muted("blue")))
```




ordinal_format Ordinal formatter: add ordinal suffixes (-st, -nd, -rd, -th) to numbers.
Description
Ordinal formatter: add ordinal suffixes (-st, -nd, -rd, -th) to numbers.
Usage
    ordinal_format(x)
    ordinal(x)
Arguments
x a numeric vector to format Value
a function with single paramater x, a numeric vector, that returns a character vector
```{r}
  ordinal_format()(1:10)
    ordinal(1:10)
```

package-scales Generic plot scaling methods
Description
Generic plot scaling methods


parse_format Parse a text label to produce expressions for plotmath. Description
Parse a text label to produce expressions for plotmath.
Usage
    parse_format()
Value
a function with single parameter x, a character vector, that returns a list of expressions


```{r}
parse_format()(c("alpha", "beta", "gamma"))
```

percent_format Percent formatter: multiply by one hundred and display percent sign.
Description
Percent formatter: multiply by one hundred and display percent sign.
Usage
    percent_format()
percent(x)
Arguments
x a numeric vector to format Value
a function with single parameter x, a numeric vector, that returns a character vector


```{r}
percent_format()(runif(10))
    percent(runif(10))
    percent(runif(10, 1, 10))
```


pretty_breaks Pretty breaks. Uses default R break algorithm as implemented in pretty.
Description
Pretty breaks. Uses default R break algorithm as implemented in pretty. Usage
    pretty_breaks(n = 5, ...)
Arguments
n desired number of breaks
... other arguments passed on to pretty

```{r}
pretty_breaks()(1:10)
pretty_breaks(n=10)(1:100)
    

```

```{r}
pretty_breaks(n=4)(as.Date(c("2008-01-01", "2009-01-01")))
```
```{r}
pretty_breaks()(as.Date(c("2008-01-01", "2090-01-01")))
```


```{r}
seq.Date(as.Date(c("2008-01-01")),as.Date(c( "2009-01-01")),"1 month")
seq.Date(as.Date(c("2008-01-01")),as.Date(c( "2009-01-01")),"2 month")
seq.Date(as.Date(c("2008-01-01")),as.Date(c( "2009-01-01")),"3 month")
```



```{r}
date=seq.Date(as.Date(c("2008-01-01")),as.Date(c( "2016-01-01")),"year")
date

```

###probability_trans Probability transformation.
Description
Probability transformation.
Usage
    probability_trans(distribution, ...)
Arguments
distribution probability distribution. Should be standard R abbreviation so that "p" + distri- bution is a valid probability density function, and "q" + distribution is a valid quantile function.
... other arguments passed on to distribution and quantile functions

###Range-class Mutable ranges.
Description
Mutable ranges have a two methods (train and reset), and make it possible to build up complete ranges with multiple passes.
reciprocal_trans Reciprocal transformation.
Description
Reciprocal transformation.
Usage
    reciprocal_trans()
###rescale Rescale numeric vector to have specified minimum and maximum.
Description
Rescale numeric vector to have specified minimum and maximum.
Usage
    rescale(x, to = c(0, 1), from = range(x, na.rm = TRUE, finite = TRUE))
Arguments
x numeric vector of values to manipulate.
to output range (numeric vector of length two)
from input range (numeric vector of length two). If not given, is calculated from the range of x

```{r}
rescale(1:100)%>%head()

```

```{r}
rescale(runif(50))%>%head()

```
```{r}
rescale(1)
```


```{r}
rescale(x=1:10, to = c(0, 5), from = range(x, na.rm = TRUE, finite = TRUE))
```
```{r}
seq(5,27.5,2.5)
```


rescale_max Rescale numeric vector to have specified maximum.
Description
Rescale numeric vector to have specified maximum.
Usage
    rescale_max(x, to = c(0, 1), from = range(x, na.rm = TRUE))
Arguments
x numeric vector of values to manipulate.
to output range (numeric vector of length two)
from input range (numeric vector of length two). If not given, is calculated from the range of x


```{r}
rescale_max(1:10)
    rescale_max(runif(10))
    rescale_max(1)
    rescale_max(x=10:20, to = c(1, 10), from = range(x, na.rm = TRUE))
```

rescale_mid
Description
Rescale numeric vector to have specified minimum, midpoint, and maximum.
  Rescale numeric vector to have specified minimum, midpoint, and maximum.
Usage
    rescale_mid(x, to = c(0, 1), from = range(x, na.rm = TRUE), mid = 0)
Arguments
x numeric vector of values to manipulate.
to output range (numeric vector of length two)
from input range (numeric vector of length two). If not given, is calculated from the range of x
mid mid-point of input range


```{r}
rescale_mid(x=20:30, to = c(0, 1), from = range(x, na.rm = TRUE), mid = 25.5)
rescale_mid(1:10, mid = 5.5)
    rescale_mid(runif(5), mid = 0.5)
    rescale_mid(1)
```

rescale_none
Description
Don’t peform rescaling
Usage
    rescale_none(x, ...)
Arguments
Don’t peform rescaling
 x numeric vector of values to manipulate. ... all other arguments ignored
 
 

```{r}
rescale_none(1:10)
```

rescale_pal Rescale palette (continuous).
Description
Just rescales the input to the specific output range. Useful for alpha, size, and continuous position.
Usage
    rescale_pal(range = c(0.1, 1))
Arguments
range Numeric vector of length two, giving range of possible values. Should be be- tween 0 and 1.
```{r}
#runif(5)%>%rescale_pal(range = c(0.1, 1))
```
reverse_trans
Description
Reverse transformation.
Usage
    reverse_trans()
  scientific_format
Description
Scientific formatter.
Usage
31
 Reverse transformation.
 ### Scientific formatter.
     scientific_format(digits = 3, ...)
    scientific(x, digits = 3, ...)
Arguments
digits number of significant digits to show ... other arguments passed on to format x a numeric vector to format
Value
a function with single parameter x, a numeric vector, that returns a character vector

```{r}
scientific_format()(1:10)
    scientific_format()(runif(10))
    scientific_format(digits = 2)(runif(10))
    scientific(1:10)
    scientific(runif(10))
    scientific(runif(10), digits = 2)
```


### seq_gradient_pal Sequential colour gradient palette (continous).
Description
Sequential colour gradient palette (continous).
Usage
    seq_gradient_pal(low = mnsl("10B 4/6"), high = mnsl("10R 4/6"),
      space = "Lab")
Arguments
low colour for low end of gradient.
high colour for high end of gradient.
space colour space in which to calculate gradient. Must be "Lab" - other values are deprecated.

```{r}
x <- seq(0, 1, length.out = 25)
    show_col(seq_gradient_pal()(x))
    show_col(seq_gradient_pal("white", "black")(x))
    library(munsell)
    show_col(seq_gradient_pal("white", mnsl("10R 4/6"))(x))
```



###shape_pal Shape palette (discrete).
Description
Shape palette (discrete).
Usage
    shape_pal(solid = TRUE)
Arguments
solid should shapes be solid or not?

###show_col Show colours.
Description
A quick and dirty way to show colours in a plot.
Usage
    show_col(colours, labels = TRUE, borders = NULL)
  Arguments
    colours
    labels
borders
###sqrt_trans
Description
a character vector of colours
boolean, whether to show the hexadecimal representation of the colours in each tile
colour of the borders of the tiles; matches the border argument of rect. The default means par("fg"). Use border = NA to omit borders.
Square-root transformation.
  Square-root transformation.
Usage
    sqrt_trans()
squish
Description
Squish values into range.
Usage
Squish values into range.
  squish(x, range = c(0, 1), only.finite = TRUE)
  
  
###  squish
Description
Squish values into range.
Usage
Squish values into range.
squish(x, range = c(0, 1), only.finite = TRUE)
 x
    range
    only.finite
Author(s)
squish_infinite
numeric vector of values to manipulate.
numeric vector of length two giving desired output range. if TRUE (the default), will only modify finite values.
```{r}

    squish(c(-1, 0.5, 1, 2, NA))
    squish(c(-1, 0, 0.5, 1, 2))
    squish(x=c(-1, 0, 0.5, 1, 2,-16,6), range = c(-5, 10), only.finite = TRUE)
```

 squish_infinite Squish infinite values to range.
Description
Squish infinite values to range.
Usage
    squish_infinite(x, range = c(0, 1))
Arguments
x numeric vector of values to manipulate.
range numeric vector of length two giving desired output range.
Examples

```{r}
squish_infinite(c(-Inf, -1, 0, 1, 2, Inf))
squish_infinite(x=c(-Inf, -1, 0, 1, 2, Inf), range = c(0, 1))
```

  
###  time_trans Transformation for date-times (class POSIXt).
Description
Transformation for date-times (class POSIXt).
Usage
    time_trans(tz = NULL)
Arguments
tz Optionally supply the time zone. If NULL, the default, the time zone will be extracted from first input with a non-null tz.

```{r}
hours <- seq(ISOdate(2000,3,20, tz = ""), by = "hour", length.out = 10)
   hours
   
```

```{r}

    t <- time_trans()
    t$transform(hours)
    
```


```{r}
t$inverse(t$transform(hours))
    
```
```{r}
t$format(t$breaks(range(hours)))
```
####train_continuous Train (update) a continuous scale
Description
Train (update) a continuous scale
Usage
    train_continuous(new, existing = NULL)
Arguments
new New data to add to scale existing Optional existing scale to update





###train_discrete Train (update) a discrete scale
Description
Train (update) a discrete scale
Usage
    train_discrete(new, existing = NULL, drop = FALSE, na.rm = FALSE)
  Arguments
    new
    existing
    drop
    na.rm
####trans_breaks
Description
These often do not
Usage
New data to add to scale
Optional existing scale to update
TRUE, will drop factor levels not associated with data If TRUE, will remove missing values
Pretty breaks on transformed scale.
produce very attractive breaks.
      trans_breaks(trans, inv, n = 5, ...)
Arguments
trans function of single variable, x, that given a numeric vector returns the transformed values
inv inverse of the transformation function n desired number of ticks
... other arguments passed on to pretty

```{r}
trans_breaks("log10", function(x) 10 ^ x)(c(1, 1e6))
    trans_breaks("sqrt", function(x) x ^ 2)(c(1, 100))
    trans_breaks(function(x) 1 / x, function(x) 1 / x)(c(1, 100))
    trans_breaks(function(x) -x, function(x) -x)(c(1, 100))
```

####trans_format Format labels after transformation.
Description
Format labels after transformation.
Usage
    trans_format(trans, format = scientific_format())
Arguments
trans transformation to apply
format additional formatter to apply after transformation
Value
a function with single parameter x, a numeric vector, that returns a character vector of list of ex- pressions

```{r}
tf <- trans_format("log10", scientific_format())
    tf(10 ^ 1:6)
```



trans_new Create a new transformation object.
Description
A transformation encapsulates a transformation and its inverse, as well as the information needed to create pleasing breaks and labels. The breaks function is applied on the transformed range of the range, and it’s expected that the labels function will perform some kind of inverse tranformation on these breaks to give them labels that are meaningful on the original scale.
Usage
    trans_new(name, transform, inverse, breaks = extended_breaks(),
      format = format_format(), domain = c(-Inf, Inf))
      
      
      
 
 
```{r}
trans_breaks("log10", function(x) 10 ^ x)(c(3))
log(1000)
logb(1000)
```

####trans_range Compute range of transformed values.
Description
Silently drops any ranges outside of the domain of trans. Usage
    trans_range(trans, x)
  Arguments
trans x
unit_format
Description
Add units to the labels
Usage
a transformation object, or the name of a transformation object given as a string. a numeric vector to compute the rande of
Add units to the labels
  unit_format(unit = "m", scale = 1, sep = " ", ...)
  
  
  
```{r}
 # labels in kilometer when the raw data are in meter
    km <- unit_format(unit = "km", scale = 1e-3, digits = 2)
    km(runif(10) * 1e3)
    # labels in hectares, raw data in square meters
    ha <- unit_format(unit = "ha", scale = 1e-4)
    km(runif(10) * 1e5)

```


wrap_format Wrap text to a specified width, adding newlines for spaces if text ex- ceeds the width
Description
Wrap text to a specified width, adding newlines for spaces if text exceeds the width
Usage
    wrap_format(width)
Arguments
width value above which to wrap Value
Function with single parameter x, a character vector, that returns a wrapped character vector
Examples
    wrap_10 <- wrap_format(10)
    wrap_10('A long line that needs to be wrapped')
```{r}
 wrap_10 <- wrap_format(10)
    wrap_10('A long line that needs to be wrapped')
```

###zero_range Determine if range of vector is close to zero, with a specified tolerance
Description
The machine epsilon is the difference between 1.0 and the next number that can be represented by the machine. By default, this function uses epsilon * 1000 as the tolerance. First it scales the values so that they have a mean of 1, and then it checks if the difference between them is larger than the tolerance.
Usage
    zero_range(x, tol = 1000 * .Machine$double.eps)
Arguments
x numeric range: vector of length 2 tol A value specifying the tolerance.
Value
logical TRUE if the relative difference of the endpoints of the range are not distinguishable from 0.

```{r}
eps <- .Machine$double.eps
    zero_range(c(1, 1 + eps))       # TRUE
    zero_range(c(1, 1 + 99 * eps))  # TRUE
    zero_range(c(1, 1 + 1001 * eps)) # FALSE - Crossed the tol threshold
    zero_range(c(1, 1 + 2 * eps), tol = eps) # FALSE - Changed tol
    # Scaling up or down all the values has no effect since the values
    # are rescaled to 1 before checking against tol
    zero_range(100000 * c(1, 1 + eps))        # TRUE
    zero_range(100000 * c(1, 1 + 1001 * eps))  # FALSE
    zero_range(.00001 * c(1, 1 + eps))        # TRUE
    zero_range(.00001 * c(1, 1 + 1001 * eps))  # FALSE
    # NA values
    zero_range(c(1, NA))   # NA
    zero_range(c(1, NaN))  # NA
    # Infinite values
    zero_range(c(1, Inf))     # FALSE
    zero_range(c(-Inf, Inf))  # FALSE
    zero_range(c(Inf, Inf))   # TRUE
```

