---
title: "Tidy Evaluation"
output:
  html_document:
    toc: true
    theme: united
author: Nana Boateng
df_print: paged
Time: '`r Sys.time()`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
number_sections: true  ## if you want number sections at each table header
highlight: tango  # specifies the syntax highlighting style

---




```{r}

pacman::p_load(tidyverse)
library(rlang)

```


quote() is the most basic quoting function

```{r}

letters[1:5]

quote(letters[1:5])


```

#### Delayed evaluation
eval() gets the value of the expression

```{r}

x <- quote(letters[1:5]) 
eval(x)

data <- list(letters = LETTERS) 
 
eval(x, data)
eval_tidy(x, data)

```

#### Programming with grammars

```{r}
#stringly(nobody, calls, me, coward) #> [1] "nobody calls me coward"
x <- "chicken" 

#stringly(nobody, calls, me, x)
#> [1] "nobody calls me x"
paste("nobody", "calls", "me", x)

#stringly(nobody, calls, me, eval(x))

```


```{r}

df <- tibble(x = 1:3, y = 3:1)

filter(df, x == 1)

x = 1:3
my_var <- enquo(x)
#> Error in eval(expr, envir, enclos): object 'x' not found
filter(df, !!(my_var) == 1)


```
#### Misssing Values

```{r}

#This infix function is similar to %||% but is vectorised and provides a default value for missing elements. It is faster than using base::ifelse() and does not perform type conversions.
c("a", "b", NA, "c") %|% "default"

#Default value for NULL
#This infix function makes it easy to replace NULLs with a default value. It's inspired by the way that Ruby's or operation (||) works.


1 %||% 2


NULL %||% 2

```


#### Quotation or Quasiqoutation

```{r}
# Quasiquotation functions quote expressions like base::quote()
quote(how_many(this))
expr(how_many(this))
quo(how_many(this))

# In addition, they support unquoting. Let's store symbols
# (i.e. object names) in variables:
this <- sym("apples")
that <- sym("oranges")
this
that


# With unquotation you can insert the contents of these variables
# inside the quoted expression:
expr(how_many(!!this))
expr(how_many(!!that))


# You can also insert values:
expr(how_many(!!(1 + 2)))
quo(how_many(!!(1 + 2)))

# This is why it's often useful to use qq_show() to examine the
# result of unquotation operators. It uses the same printer as
# quosures but does not return anything:
qq_show(how_many(!!(1:10)))

```

```{r}
# Use `!!!` to add multiple arguments to a function. Its argument
# should evaluate to a list or vector:
args <- list(1:3, na.rm = TRUE)
quo(mean(!!!args))

```



#### Capturing multiple variables
It would be nice to extend my_summarise() to accept any number of grouping variables. We need to make three changes:

Use ... in the function definition so our function can accept any number of arguments.

Use quos() to capture all the ... as a list of formulas.

Use !!! instead of !! to splice the arguments into group_by().

```{r}
df <- tibble(
  g1 = c(1, 1, 2, 2, 2),
  g2 = c(1, 2, 1, 2, 1),
  a = sample(5),
  b = sample(5)
)

my_summarise <- function(df, ...) {
  group_var <- quos(...)

  df %>%
    group_by(!!! group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, g1, g2)

```

```{r}
f <- function(x) {
  quo(x)
}

x1 <- f(10)
x2 <- f(100)

x1
x2


get_env(x1)

get_env(x2)

eval_tidy(x1)

eval_tidy(x2)

```

```{r}

```

