---
title: "Update R"
output:
  html_document:
    toc: true
    theme: united
author: Nana Boateng
df_print: paged
Time: '`r Sys.time()`'
date: "`r format(Sys.time(), '%B %d, %Y')`"
toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
number_sections: true  ## if you want number sections at each table header
highlight: tango  # specifies the syntax highlighting style

---



```{r setup,include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      out.width ="100%",
                      message = FALSE,
                      fig.align = 'default', 
                      warning = FALSE, 
                      fig.cap ="Fig. 30", 
                      out.width="100%")

options(repr.plot.height = 10, repr.plot.width = 8)
options(tidyverse.quiet = TRUE)
options(dplyr.print_max = 1e9)
knitr::opts_knit$set(root.dir = normalizePath("/Users/nanaakwasiabayieboateng/Documents/memphisclassesbooks/Time series/Manpower/")) 
#knitr::read_chunk("example.R")

```



Update R
---------------------------------

```{r}
library(devtools)

#install_github('andreacirilloac/updateR')

library(updateR)

updateR(admin_password = 'abayie148')
```

check rstudio version
```{r}
 version
```


now you can update your packages by typing update.packages() in your RStudio console, and answering 'y' to all of the prompts.
```{r}
update.packages(checkBuilt=TRUE)
```



```{r}
# How to update R in RStudio using installr package (for Windows)
## paste this into the console and run the commands
## "The updateR() command performs the following: finding the latest R version, downloading it, running the installer, deleting the installation file, copy and updating old packages to the new R installation."
## more info here: https://cran.r-project.org/web/packages/installr/index.html

install.packages("installr")
library(installr)
updateR()

## Watch for small pop up windows. There will be many questions and they don't always pop to the front. 
## Note: It warns that it might work better in Rgui but I did it in Rstudio and it worked just fine. 

#installing/loading the package:
if(!require(installr)) {
install.packages("installr"); require(installr)} #load / install+load installr

# using the package:
updateR() # this will start the updating process of your R installation.  It will check for newer versions, and if one is available, will guide you through the decisions you'd need to make.
```


Linux/MacOS ->> Open a terminal and type "R" to go into interactive mode and then:

```{r}
lib_path <- Sys.getenv("R_LIBS_USER")
install.packages("installr", lib = lib_path)
install.packages("stringr", lib_path)
library(stringr, lib.loc = lib_path)
library(installr, lib.loc = lib_path)
installr::updateR()
```



Updating R Packages
Updating Out of date Packages
Updating out of date package that were installed with install.packages() is easy with the update.packages() function.

update.packages()
Which will ask you for every package if you want to update, to just say yes to everything use ask = FAlSE.

update.packages(ask = FALSE)
Unfortunately this won’t update packages installed by devtools::install_github()

Updating all Packages after R update
On Windows this is hanlded by the package installr. But for other operating systems, after updating R, a lot of packages might have been build under the old R version and it would be safer to re-install all the packages already installed. This can be done with the following commands. Again this won’t update packages installed with devtools::install_github()

## get packages installed
packs = as.data.frame(installed.packages(.libPaths()[1]), stringsAsFactors = F)

## and now re-install install packages using install.packages()
install.packages(packs$Package)